### 2015-06-14 paper/paper.tex
Have general structure for the paper
- tex file written
- empty bibliography file written

\documentclass{article}

\usepackage{fullpage}
\usepackage[parfill]{parskip}

\usepackage[backend=biber,firstinits=true , backref=false, url=true, isbn=true]{biblatex}
\addbibresource{library.bib}

\title{Playing Games: A Case Study in Active Learning}
\author{Vince Knight}
\date{\today}

\begin{document}

\maketitle

\abstract{
A paper about active learning and using some example of this in a class on Game Theory
}

\section{Introduction}

\begin{itemize}
    \item Describe active learning briefly;
    \item Describe variety of techniques
    \item Mention lack of how to's
    \item Describe structure of paper
\end{itemize}

\section{Overview of Active Learning}

\begin{itemize}
    \item reference literature
    \item show some results
\end{itemize}

\section{An exemplar: a course in game theory}

\begin{itemize}
    \item Discuss other examples of how game theory is taught
    \item Describe this course
    \item Give description of the general philosophy of the course (no content:
        purely examples, which give data for games)
\end{itemize}

\subsection{Mixed strategies}

\begin{itemize}
    \item Some of the theory
    \item Playing v machine
    \item RPSLS tournament
\end{itemize}

\subsection{Repeated and random games}

\begin{itemize}
    \item The theory
    \item Tournaments: 1, 2 and 3.
\end{itemize}

\subsection{Cooperative games}

\begin{itemize}
    \item The theory
    \item Explain the idea.
\end{itemize}

\section{Summary}

\begin{itemize}
    \item Give some examples of feedback.
    \item Mention how methods could be applied to other courses.
    \item Certain class management ideas (mainly that I will not speak first a
        lot of the time) <- Not sure if this is useful.
\end{itemize}

\printbibliography
\end{document}

### 2015-06-21 paper/paper.tex
First draft of introduction written.
Mainly have references describing what active learning is.

@@
-\documentclass{article}
-
-\usepackage{fullpage}
-\usepackage[parfill]{parskip}
+\documentclass[a4paper]{article}
 
@@
 
-\title{Playing Games: A Case Study in Active Learning}
+\usepackage{fullpage} % Package to use full page
+\usepackage{amsmath}
+\usepackage{hyperref}
+
+\title{Playing Games: A Case Study in Active Learning Applied to Game Theory}
 \author{Vince Knight}
@@
 
+Modern pedagogic theories as to how learning takes place such as constructivism
+and socialism \cite{Illeris2009, Jordan2008a}, indicate that an \textbf{active
+learning} approach is of benefit to student learning.  As stated in
+\cite{Prince2004} there are a variety of complementary definitions of active
+learning, however the general definition given in \cite{Prince2004} is the one
+assumed in this paper:
+
+\begin{quote}
+``Active learning is generally defined as any instructional method that engages
+students in the learning process. In short active learning requires students to
+do meaningful learning activities and think about what they are doing.''
+\end{quote}
+
+One could argue that all learning is active as students simply listening to a
+lecture are perhaps taking part in a `meaningful learning activity', however as
+stated in \cite{Bonwell1991} active learning is understood to imply that
+students:
+
 \begin{itemize}
-    \item Describe active learning briefly;
-    \item Describe variety of techniques
-    \item Mention lack of how to's
-    \item Describe structure of paper
+    \item read, write, discuss, or engage in solving problems;
+    \item engage in higher order tasks such as analysis, synthesis and
+        evaluation.
 \end{itemize}
 
-\section{Overview of Active Learning}
+A variety of studies have highlighted the effectiveness of active learning
+\cite{Freeman2014, Hake1998, Prince2004}. These two papers are in fact meta studies
+evaluating the effectiveness an active student centred approach. Note that the
+definition used in \cite{Freeman2014} corresponds to simply any pedagogic
+approach in which students are not passive consumers of a lecture during the
+class meeting.
+
+Some examples of active learning in a variety of subjects include:
 
 \begin{itemize}
-    \item reference literature
-    \item show some results
+    \item The flipped learning environment in a Physics class: \cite{Bates}.
+    \item Inquiry based learning for the instruction of differential equations:
+        \cite{Kwon2005}.
+    \item Using collaborative learning in a pharmacology class:
+        \cite{Depaz2008}.
 \end{itemize}
+
+The above sources (and references therein) generally discuss the pedagogic
+approach from a macroscopic point of view with regards to the course considered.
+This manuscript will give a detailed description of two particular active
+learning activities used in the instruction of Game Theoretic concepts.
 
@@
 
-\subsection{Mixed strategies}
+\subsection{Best responses}
 
 \begin{itemize}
-    \item Some of the theory
-    \item Playing v machine
-    \item RPSLS tournament
+    \item The two thirds of the average game: how this is a basic game
+    \item How it is played in class
+    \item Description of data and discussion that ensues
 \end{itemize}
@@
     \item The theory
-    \item Tournaments: 1, 2 and 3.
+    \item Tournaments:
+        \begin{itemize}
+            \item Basic type.
+            \item Infinitely repeated game.
+            \item Markov games.
         \end{itemize}
-
-\subsection{Cooperative games}
-
-\begin{itemize}
-    \item The theory
-    \item Explain the idea.
 \end{itemize}

### 2015-06-21 paper/paper.tex
Initial description of two thirds game done.

@@
-\documentclass[a4paper]{article}
+\documentclass{article}
 
@@
 approach in which students are not passive consumers of a lecture during the
-class meeting.
-
-Some examples of active learning in a variety of subjects include:
+class meeting. Some examples of active learning in a variety of subjects include:
 
@@
 This manuscript will give a detailed description of two particular active
-learning activities used in the instruction of Game Theoretic concepts.
-
-\section{An exemplar: a course in game theory}
+learning activities used in the instruction of Game Theoretic concepts:
 
 \begin{itemize}
-    \item Discuss other examples of how game theory is taught
-    \item Describe this course
-    \item Give description of the general philosophy of the course (no content:
-        purely examples, which give data for games)
+    \item Section \ref{sec:best_responses} will describe an in class activity
+        and software package used to introduce students to the topic of best
+        response dynamic \cite{Maschler2013}.
+    \item Section \ref{sec:repeated_games} will describe an implementation of
+        Axelrod's tournament \cite{Axelrod1980a,Axelrod1980a}.
 \end{itemize}
 
-\subsection{Best responses}
+These activities aim to introduce the student to the concepts and aspire to
+their curiosity as to the underlying mathematics. Note that if there is any
+doubt as to the effectiveness of active learning approaches, for example this paper
+(the only one that this author could identify) \cite{Andrews2011} identifies no
+such relationship are still beneficial to the students' learning.
+Indeed in \cite{Poropat2014}  the greatest predictors of
+academic performance are identified not as general intelligence \cite{Wright1905} but
+personality factors such as conscientiousness and openness.
+
+\section{An exemplar: a course in game theory}\label{sec:game_theory}
+
+Game Theory as a topic is well suited to approaches that use activities
+involving students as players to introduce the concepts, rules and strategies
+for particular games and/or theorems presented.
+
+In \cite{Brokaw2004} one such activity is presented: a game that allow players
+to grasp the concept of common knowledge of rationality. Another good example is
+\cite{Polak2008}: Yale's Professor Polak's course, the videos available at that
+reference (a YouTube playlist) all show that students are introduced to every
+concept through activity before discussing theory.
+
+Just as the activity presented in \cite{Brokaw2004} the activities presented
+here are both suited for as an early introduction to the concepts (although the
+activity of Section \ref{sec:repeated_games} is potentially better suited to
+being used at a later stage). Furthermore, these activities have also been used
+as outreach activities for high school students with no knowledge of further
+mathematics.
+
+\subsection{Best response dynamics}\label{sec:best_responses}
+
+The first step in this activity and potentially before any prior description of
+Game Theory students are invited to answer the following simple question:
+
+\begin{center}
+    \textbf{What is a game?}
+\end{center}
+
+Through discussion the class will usually arrive at the following consensus:
 
 \begin{itemize}
-    \item The two thirds of the average game: how this is a basic game
-    \item How it is played in class
-    \item Description of data and discussion that ensues
+    \item A game must have a certain number \(N\geq 1\) of players;
+    \item Each player must have available to them a certain number of strategies
+        that define what they can do;
+    \item Once all players have chosen their strategy, rules must specify what
+        the outcome is.
 \end{itemize}
 
-\subsection{Repeated and random games}
+This corresponds to the general definition of a strategic form game
+\cite{Maschler2013}. The main goal of this activity is to not only understand
+the vocabulary but also the important concept of response dynamics which aims
+to identify what is the best option given prior knowledge of all other players
+\cite{Maschler2013}. One particular game that can be analysed using base
+response dynamics is often referred to:
+
+\begin{center}
+    \textbf{The two thirds of the average game.}
+\end{center}
+
+A good description of the game and the human dynamics associated to the play is
+given in \cite{Nagel1995}. The rules are as follows:
+
+\begin{itemize}
+    \item All players choose a number between 0 and 100;
+    \item The player whose choice was closest to \(\frac{2}{3}\) of the average
+        of the choices wins.
+\end{itemize}
+
+The activity is similar to the activity described in
+\cite{TheEconomicsNetwork2013}:
+
+\begin{enumerate}
+    \item Students are handed out copies of the form available at URL
+    \item Students are explained the rules of the game and invited to play a
+        first guess.
+    \item After this the class is explained the rationalisation of the game
+        (which uses best response dynamics to iteratively eliminate dominated
+        strategies) as shown in Figure
+        \ref{fig:rationalisation_of_two_thirds_game}.
+    \item Students are invited to play one more time.
+    \item Results are analysed and presented to the class for discussion.
+\end{enumerate}
+
+\subsection{Repeated and random games}\label{sec:repeated_games}
 

### 2015-06-28 paper/paper.tex
Adding rationalisation picture

@@
 \usepackage{hyperref}
+\usepackage{tikz}
 
@@
 A good description of the game and the human dynamics associated to the play is
-given in \cite{Nagel1995}. The rules are as follows:
+given in \cite{Nagel1995}.  The use of this game in teaching is not novel in
+game theory \cite{TheEconomicsNetwork2013}
+The rules are as follows:
 
@@
 
-The activity is similar to the activity described in
-\cite{TheEconomicsNetwork2013}:
+To make use of this game in class as an introduction to the concept of best
+response dynamics students are handed a sheet of paper inviting them to write
+down a first play. After this initial play, a discussion is had that
+demonstrates that the equilibrium for this game is for all players to guess 0.
+This is shown diagrammatically in Figure
+\ref{fig:rationalisation_of_two_thirds_game}.
+Following this discussion students are invited to play again and write down
+their second guess.
 
-\begin{enumerate}
-    \item Students are handed out copies of the form available at URL
-    \item Students are explained the rules of the game and invited to play a
-        first guess.
-    \item After this the class is explained the rationalisation of the game
-        (which uses best response dynamics to iteratively eliminate dominated
-        strategies) as shown in Figure
-        \ref{fig:rationalisation_of_two_thirds_game}.
-    \item Students are invited to play one more time.
-    \item Results are analysed and presented to the class for discussion.
-\end{enumerate}
+\begin{figure}
+    \begin{center}
+        \begin{tikzpicture}
+            % First level of play
+            \node (0) at (0,0) {$0$};
+            \node (100) at (10,0) {$100$};
+            \draw [thick] (0) -- (100);
+            \node [below] at (6.7,0) {$67$};
+
+            % Getting rid of dominated strategies
+            \foreach \x in {7, 7.3, 7.6, 7.9, 8.2, 8.5, 8.8, 9.1, 9.4}
+            {
+                \draw [blue!80, very thick] (\x,-.25) -- (\x + .2,.25);
+            }
+            \draw [very thick, blue!80] (9, -.5) edge[out=270,in=0,->] (7, -2);
+
+                % Second level of play
+                \node (0) at (0,-2) {$0$};
+                \node (67) at (6.7,-2) {$67$};
+                \draw [thick] (0) -- (67);
+                \node [below] at (4.4,-2) {$44$};
+
+                % Getting rid of dominated strategies
+                \foreach \x in {4.7, 5, 5.3, 5.6, 5.9, 6.2}
+                {
+                    \draw [blue!60, very thick] (\x,-2.25) -- (\x + .2,-1.75);
+                }
+                \draw [very thick, blue!60] (6, -2.5) edge[out=270,in=0,->] (4.7, -4);
+
+                    % Third level of play
+                    \node (0) at (0,-4) {$0$};
+                    \node (44) at (4.4,-4) {$44$};
+                    \draw [thick] (0) -- (44);
+                    \node [below] at (2.9,-4) {$29$};
+
+                    % Getting rid of dominated strategies
+                    \foreach \x in {3.2, 3.5, 3.8}
+                    {
+                        \draw [blue!40, very thick] (\x,-4.25) -- (\x + .2,-3.75);
+                    }
+
+                        % Final level of play
+                        \node at (2, -5) {\dots};
+                        \node (0) at (1,-6) [draw] {$0$};
+                        \draw [very thick, blue!40] (3.4, -4.5) edge[out=270,in=0,->] (1.5, -6);
+
+            \node at (8, -5) [draw] {Removing dominated strategies};
+        \end{tikzpicture}
+    \end{center}
+    \caption{Equilibrium behaviour in the two thirds of the average
+    game}\label{fig:rationalisation_of_two_thirds_game}
+\end{figure}
 

### 2015-06-29 paper/paper.tex
Updating document and plot
- Including a plot showing results only for students who reduce their
  guess
- Adding to text describing this.

@@
 \usepackage{tikz}
+\usepackage{subcaption}
 
@@
     \item Section \ref{sec:repeated_games} will describe an implementation of
-        Axelrod's tournament \cite{Axelrod1980a,Axelrod1980a}.
+        Axelrod's tournament \cite{Axelrod1980a, Axelrod1980b}.
 \end{itemize}
@@
 \ref{fig:rationalisation_of_two_thirds_game}.
+
 Following this discussion students are invited to play again and write down
-their second guess.
+their second guess. All of the results are collected, the author has used paper
+forms but an automated approach could also be used. In general the input and
+analysis of the data takes less than 10 minutes and can be done by a helper
+during another class activity.
+Following this, the result shown in Figure \ref{fig:histogram_of_guess} are
+shown and discussed with the class.
 
@@
 
+The author has used this activity on a large number of occasions and at all
+times collected the data. Figure \ref{fig:histogram_of_guess} shows the
+distribution of the guesses (depending on the round of play):
+
+\begin{figure}[htpb]
+    \begin{subfigure}{.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../data/histogram_of_guesses.pdf}
+        \caption{Frequency of guesses depending on the round of play.}
+        \label{fig:histogram_of_guess}
+    \end{subfigure}
+    \begin{subfigure}{.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../data/jointplot_of_guesses.pdf}
+        \caption{Linear relationship between guesses of each round of play.}
+        \label{fig:jointplot_of_guess}
+    \end{subfigure}
+    \caption{Results from all data collected.}
+    \label{fig:all_results}
+\end{figure}
+
+We see that the second round (after the rationalisation of play described in
+Figure \ref{fig:rationalisation_of_two_thirds_game}) has guesses that are closer
+to the expected equilibrium behaviour.
+Figure \ref{fig:jointplot_of_guess} confirms this showing the linear
+relationship (albeit a weak one with \(R^2=.2\)):
+
+\begin{equation}
+    (\text{Second guess}) = .203\times(\text{First guess}) + 9.45
+    \label{eq:linear_relationship}
+\end{equation}
+
+The fact that the coefficient of the relationship is less than one highlights
+that the second guess is in general lower than the first guess. As can be seen
+in Figure \ref{fig:all_results} not all students reduce their guess. Figure
+\ref{fig:results_with_decreasing_guess} shows the results when removing these
+irrational moves. In this particular case the linear relationship is in fact
+stronger \(R^2=.43\):
+
+\begin{equation}
+    (\text{Second guess}) = .33\times(\text{First guess}) + 0.20
+    \label{eq:linear_relationship}
+\end{equation}
+
+\begin{figure}[htpb]
+    \begin{subfigure}{.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../data/histogram_of_guesses_removing_increasing_guesses.pdf}
+        \caption{Frequency of guesses depending on the round of play.}
+        \label{fig:histogram_of_guess}
+    \end{subfigure}
+    \begin{subfigure}{.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../data/jointplot_of_guesses_removing_increasing_guesses.pdf}
+        \caption{Linear relationship between guesses of each round of play.}
+        \label{fig:jointplot_of_guess}
+    \end{subfigure}
+    \caption{Results from data when removing increasing guesses.}
+    \label{fig:results_with_decreasing_guess}
+\end{figure}
+
+At the end of the activity, students are shown the graphical results and a
+discussion had about why the theoretic equilibrium was not the winner. This
+discussion usually revolves around the observation that not everyone acted
+rationally and second that some participants felt like they should `spoil' the
+game by guessing larger in the second round.
+
+Finally, if time permits (and depending on the level of the participants), the
+linear relationship of (\ref{eq:linear_relationship}) is used to discuss what
+would happen if more rounds were to be played. In particular it is possible to
+discuss ideas of convergence when generalising (\ref{eq:linear_relationship}) to
+be:
+
+\begin{equation}
+    \text{Guess}_{n+1} = .203\times\text{Guess}_n + 9.45
+    \label{eq:extrapolated_linear_relationship}
+\end{equation}
+
 \subsection{Repeated and random games}\label{sec:repeated_games}

### 2015-06-29 paper/paper.tex
Adding summary of approach - need discussion about participation

@@
     (\text{Second guess}) = .33\times(\text{First guess}) + 0.20
-    \label{eq:linear_relationship}
+    \label{eq:linear_relationship_for_increasing_guesses}
 \end{equation}
@@
 
+To summarise this activity:
+
+\begin{enumerate}
+    \item Participants are explained the rules and play one round of the two
+        thirds of the average game.
+    \item A rationalisation and explanation of equilibrium behaviour is
+        described.
+    \item Participants play another round.
+    \item Results are analysed and discussed.
+\end{enumerate}
+
+This activity is still quite passive in terms of physical activity (participants are
+seated throughout). Nevertheless it allows the data used for the discussion of
+the theory to come directly from the participants.
+
 \subsection{Repeated and random games}\label{sec:repeated_games}

### 2015-06-29 paper/paper.tex
Starting to write section about repeated games.

@@
 seated throughout). Nevertheless it allows the data used for the discussion of
-the theory to come directly from the participants.
+the theory to come directly from the participants and further more all students
+are active participants and there are no difficulties with regards to
+encouraging participation (references to these are discussed in \cite{Rocca2010}).
 
 \subsection{Repeated and random games}\label{sec:repeated_games}
+
+This activity is used to introduce students to the concepts of repeated games
 

### 2015-06-29 paper/paper.tex
Including the wordlike package
Journal requires submission via word.
1st draft of section on Axelrod activity now written.
Various pieces missing.

@@
 
-\usepackage{fullpage} % Package to use full page
 \usepackage{amsmath}
@@
 \usepackage{tikz}
+\usepackage{booktabs}
 \usepackage{subcaption}
+
+\usepackage{wordlike}  % Make this look like word made it
 
@@
 
-\begin{figure}
+\begin{figure}[!hbtp]
     \begin{center}
@@
 
-\begin{figure}[htpb]
+\begin{figure}[!hbtp]
     \begin{subfigure}{.6\textwidth}
@@
 This activity is used to introduce students to the concepts of repeated games
+\cite{Maschler2013}. The mathematical details can be omitted from the initial
+description of the activity to the participants but for completeness it they are
+included here:
 
-\begin{itemize}
-    \item The theory
-    \item Tournaments:
-        \begin{itemize}
-            \item Basic type.
-            \item Infinitely repeated game.
-            \item Markov games.
-        \end{itemize}
-\end{itemize}
+A repeated game is played over discrete time periods. Each time period is
+indexed by \(0<t\leq T\) where \(T\) is the total number of periods.  In each
+period \(N\) players play a static game referred to as the \textbf{stage game}
+independently and simultaneously selecting actions.  Players make decisions in
+full knowledge of the \textbf{history} of the game played so far (ie the actions
+chosen by each player in each previous time period).  The payoff is defined
+as the sum of the utilities in each stage game for every time period.
+
+One of the most renowned repeated games is referred to as \textbf{Axelrod's
+tournament} which is what is recreated in this activity \cite{Axelrod1980a,
+Axelrod1980b}.
+
+Initially a description of the prisoner's dilemma \cite{Maschler2013} is given.
+The prisoner's dilemma is a simple two player game that is often used to
+introduce the very basic notions of game theory. It is described by the
+following two matrices:
+
+\[
+    A =
+    \begin{pmatrix}
+        3&5\\
+        0&1
+    \end{pmatrix}
+    \qquad
+    B =
+    \begin{pmatrix}
+        3&0\\
+        5&1
+    \end{pmatrix}
+\]
+
+The row player has utility given by \(A\) and the column player has utilities
+given by \(B\).
+The strategies available to each player are to cooperate: \(C\) or to defect:
+\(D\). Playing \(C\) corresponds to players choosing their first row/column and
+\(D\), the second row/column.
+
+Thus if both players cooperate they both receive a utility of 3, if one player
+defects, the defector gets a utility of 5 and the cooperator a utility of 0.
+Finally if both players defect they receive a utility of 1. As players (in this
+framework) aim to maximise their score, the Nash equilibrium for this game is
+for both players to defect.
+
+After describing this activity and in particular explaining the simple
+mathematical idea of \textbf{dominated strategy} (which is what is used in the
+activity of Section \ref{sec:best_responses}) participants are made aware of the
+concept of Nash equilibrium. This in turn can lead to a brief description of the
+tragic yet brilliant life of John Nash.
+
+At this point the activity is described:
+
+\begin{enumerate}
+    \item All participants will form four groups/teams;
+    \item Teams will \textit{duel} each other in repetitions of 5 to 8 rounds
+        (depending on available time).
+    \item All teams will play in a round robin tournament with cumulative scores
+        being recorded.
+    \item The victorious team will be the team with the highest total score.
+\end{enumerate}
+
+The tournament is run with all participants present (even those not watching).
+All participants are invited to stand and confer in their teams. The importance
+of standing (as a physical activity) is noted in \cite{Donnelly2011} (whilst
+that reference is mainly concerned with the impact of activity on physical well
+being it also describes advantages in terms of concentration).  Before every
+round of every duel opposing teams are encouraged to discuss strategies, after
+which they do not face each other and following a prompt hold up a card
+indicating either \(C\) or \(D\).  Duels are recorded on the white board in a
+table similar to the one shown in Table \ref{tab:duel}, in which two strategies
+constantly cooperate (thus obtaining a utility of 3 in each round). Table
+\ref{tab:duel_1} shows an example where a strategy that is alternating plays
+against a strategy that always defects.
+
+\begin{table}[!htbp]
+    \caption{Playing Tit For Tat against Cooperator}
+    \centering
+    \begin{tabular}{ccccc}
+        \toprule
+        3&6&9&12&15\\
+        \midrule
+        3&6&9&12&15\\
+        \bottomrule
+    \end{tabular}
+    \label{tab:duel}
+\end{table}
+
+\begin{table}[!htbp]
+    \caption{Playing Alternator against Defector}
+    \centering
+    \begin{tabular}{ccccc}
+        \toprule
+        5&6&11&12&17\\
+        \midrule
+        0&1&1&2&2\\
+        \bottomrule
+    \end{tabular}
+    \label{tab:duel_1}
+\end{table}
+
+The names of the strategies shown in Tables \ref{tab:duel} and \ref{tab:duel_1}
+are strategies that were used in the original tournaments run by Axelrod
+\cite{Axelrod1980a, Axelrod1980b}. The interesting fact of repeated games and
+one that becomes apparent to participants through the activity is that whilst
+repeating the stage Nash equilibrium (always defect) is indeed a Nash
+equilibrium for the repeated games, this equilibrium is not unique as
+reputation now has a part to play.
+
+Note that if students do not realise this it is important to remind them that
+the goal is not to win each duel but to obtain a high score. Often during the
+tournament one team will (during the pre round discussion) exclaim:
+
+\begin{quote}
+   ``We will cooperate until you defect, at which point we will defect
+throughout''
+\end{quote}
+
+Without realising it the participants have described a well known strategy
+(\textbf{Grudger}) which takes in to account the entire history of play.
+Figure \ref{fig:} shows a photo of a final board for a particular implementation
+of this activity.
+
+This activity can be complemented with a demonstration of software that allows
+for the rapid simulation of Axelrod's tournament \cite{Knight2015}. Figure
+\ref{fig:evolutionary_axelrod} shows the performance of the strategies when put
+in an evolutionary context.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.6\textwidth]{static/basic_strategies-reproduce.pdf}
+    \caption{Repeated games in an evolutionary context}
+    \label{fig:evolutionary_axelrod}
+\end{figure}
+
+Weakness about all participants observing...
+
+As well as being enjoyable this activity is a good intro to...
+
+Furthermore can be modified to study ...
 

### 2015-06-30 paper/paper.tex
Adding image of white board.

@@
 
-\usepackage[backend=biber,firstinits=true , backref=false, url=true, isbn=true]{biblatex}
+\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true]{biblatex}
 \addbibresource{library.bib}
@@
     \begin{center}
-        \begin{tikzpicture}
+        \begin{tikzpicture}[thick,scale=0.7, every node/.style={scale=0.7}]
             % First level of play
@@
         \centering
-        \includegraphics[width=\textwidth]{../data/histogram_of_guesses.pdf}
+        \includegraphics[width=\textwidth]{static/histogram_of_guesses.pdf}
         \caption{Frequency of guesses depending on the round of play.}
@@
         \centering
-        \includegraphics[width=\textwidth]{../data/jointplot_of_guesses.pdf}
+        \includegraphics[width=\textwidth]{static/jointplot_of_guesses.pdf}
         \caption{Linear relationship between guesses of each round of play.}
@@
         \centering
-        \includegraphics[width=\textwidth]{../data/histogram_of_guesses_removing_increasing_guesses.pdf}
+        \includegraphics[width=\textwidth]{static/histogram_of_guesses_removing_increasing_guesses.pdf}
         \caption{Frequency of guesses depending on the round of play.}
@@
         \centering
-        \includegraphics[width=\textwidth]{../data/jointplot_of_guesses_removing_increasing_guesses.pdf}
+        \includegraphics[width=\textwidth]{static/jointplot_of_guesses_removing_increasing_guesses.pdf}
         \caption{Linear relationship between guesses of each round of play.}
@@
 
+Figure \ref{fig:white_board} shows a photo of a final board for a particular
+implementation of this activity.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.5\textwidth]{static/white_board.jpg}
+    \caption{A photo of an actual implementation of the tournament.}
+    \label{fig:white_board}
+\end{figure}
+
 The names of the strategies shown in Tables \ref{tab:duel} and \ref{tab:duel_1}
@@
 (\textbf{Grudger}) which takes in to account the entire history of play.
-Figure \ref{fig:} shows a photo of a final board for a particular implementation
-of this activity.
 
 This activity can be complemented with a demonstration of software that allows
-for the rapid simulation of Axelrod's tournament \cite{Knight2015}. Figure
-\ref{fig:evolutionary_axelrod} shows the performance of the strategies when put
-in an evolutionary context.
+for the rapid simulation of Axelrod's tournament
+\cite{Axelrod-Pythonprojectteam2015}. Figure \ref{fig:evolutionary_axelrod}
+shows the performance of the strategies when put in an evolutionary context.
 
@@
     \includegraphics[width=.6\textwidth]{static/basic_strategies-reproduce.pdf}
-    \caption{Repeated games in an evolutionary context}
+    \caption{Repeated games in an evolutionary context.}
     \label{fig:evolutionary_axelrod}
@@
 
-Weakness about all participants observing...
+One of the weaknesses of this approach is that all participants observe the play
+by all the teams. Whilst from a mathematical perspective reputation is inferred
+to mean the reputation gained during a particular duel, this has the effect of
+teams being able to observe how other teams seem to play. A true replication of
+Axelrod's tournament would not allow for this. One possibility would invite
+participants to leave the room which might be logistically constrained. From a
+pedagogic point of view however, having participants observe the duels often
+leads to a much more engaged discussion (after as well as during the activity).
 
-As well as being enjoyable this activity is a good intro to...
+This activity is usually very enjoyable and leads to a lively discussion.
+Further to the fun had by participants, the theoretic discussion about repeated
+games can be placed in the exact context of the tournament that was just played.
 
-Furthermore can be modified to study ...
+This tournament can be used to introduce further game theoretic topics with
+slight modifications:
+
+\begin{itemize}
+    \item \textbf{Infinitely repeated games with discounting}: the discount
+        factor can be interpreted as a probability of the duel continuing for
+        another round (this can be randomly sampled).
+    \item \textbf{Markov games}: the two random game states can be a true game
+        and an absorbing game so that this corresponds to an infinite game with
+        discounting.
+    \item \textbf{Evolutionary games}: the two random game states can be a true game
+        and an absorbing game so that this corresponds to an infinite game with
+        discounting.
+\end{itemize}
 

### 2015-06-30 paper/paper.tex
Seaborn version of the axelrod plot.

@@
 
-\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true]{biblatex}
+\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
+%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
+%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=authoryear]{biblatex}
 \addbibresource{library.bib}
@@
 
-One of the weaknesses of this approach is that all participants observe the play
-by all the teams. Whilst from a mathematical perspective reputation is inferred
-to mean the reputation gained during a particular duel, this has the effect of
-teams being able to observe how other teams seem to play. A true replication of
-Axelrod's tournament would not allow for this. One possibility would invite
-participants to leave the room which might be logistically constrained. From a
-pedagogic point of view however, having participants observe the duels often
-leads to a much more engaged discussion (after as well as during the activity).
+One of the inconsistancies of this approach is that all participants observe the
+play by all the teams. Whilst from a mathematical perspective reputation is
+inferred to mean the reputation gained during a particular duel, this has the
+effect of teams being able to observe how other teams seem to play. A true
+replication of Axelrod's tournament would not allow for this. One possibility
+would invite participants to leave the room which might be logistically
+constrained. From a pedagogic point of view however, having participants observe
+the duels often leads to a much more engaged discussion (after as well as during
+the activity).
 
@@
 
-This tournament can be used to introduce further game theoretic topics with
+This activity can be used to introduce further game theoretic topics with
 slight modifications:

### 2015-06-30 paper/paper.tex
First draft complete
- Summary written
- Abstract written

Thorough read through required.

@@
 \usepackage{hyperref}
-\usepackage{tikz}
 \usepackage{booktabs}
@@
 \usepackage{wordlike}  % Make this look like word made it
+
+% Diagrams
+\usepackage{tikz}
+\usetikzlibrary{calc}
 
@@
 \abstract{
-A paper about active learning and using some example of this in a class on Game Theory
+    This paper describes two active learning activities aiming to introduce
+    students to the theoretic concepts of best response dynamics and repeated
+    game analysis.
+
+    An overview of some literature on active learning and the benefits therein
+    is also provided. This highlights that activities such as the one described
+    in this manuscript not only help engage students but more importantly
+    improve their learning and understanding.
+
+    The final section of the work describes how these activities fit in the
+    pedagogic framework of a particular class. Students generate data that
+    can be used as context for the understanding of theoretic concepts. It is
+    suggested that this framework is not restricted to the subject of game
+    theory.
 }
 
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 
@@
 
-One of the inconsistancies of this approach is that all participants observe the
+One of the inconsistencies of this approach is that all participants observe the
 play by all the teams. Whilst from a mathematical perspective reputation is
@@
 
-\section{Summary}
+\section{Summary and place within a pedagogic framework}\label{sec:summary}
+
+These activities have been used by the author during outreach events during
+which students take part in the activity of Section \ref{sec:best_responses} and
+whilst the results of that are being analysed take part in the activity of
+Section \ref{sec:repeated_games}. These two activities complement themselves and
+form an accessible introduction to novel mathematical topics for a wide range of
+age groups.
+
+More notably however these activities have been used as part of a family of
+activities used in a final year undergraduate course. This particular course is
+taught in active learning pedagogic framework akin to a flipped class where
+students are introduced to theoretic concepts through prior `playing of games'.
+Other examples of these activities include:
 
 \begin{itemize}
-    \item Give some examples of feedback.
-    \item Mention how methods could be applied to other courses.
-    \item Certain class management ideas (mainly that I will not speak first a
-        lot of the time) <- Not sure if this is useful.
+    \item \textbf{A rock paper scissors lizard tournament}: this serves as an
+        introduction to mixed strategies.
+    \item \textbf{A variety of games using coin flips}: this serves as an
+        introduction to game with incomplete information.
+    \item \textbf{Playing paper bin basketball in teams}: this serves as an
+        introduction to cooperative game theory.
 \end{itemize}
+
+The general pedagogical basis for this is discussed in Section
+\ref{sec:introduction} and the particular framework is shown in Figure
+\ref{fig:use_of_data}. Students are active participants in the creation of
+`data' which drives a discussion:
+
+\begin{itemize}
+    \item Why did you all guess this?
+    \item Why did that team say that on that particular occasion?
+    \item What would be a fair way of sharing the spoils for this particular
+        game?
+\end{itemize}
+
+Following that discussion the theory can be put in context by highlighting
+particular theoretic results and how they correspond (or not) to the behaviour
+exhibited during the activity. Furthermore, this encourages an immediate
+feedback with regards to student comprehension which can be reactively
+addressed.
+
+\begin{figure}[!hbtp]
+    \begin{tikzpicture}
+        % Nodes
+        \node (activity) at (0,0) [fill=cyan!30, draw] {Activity};
+        \node (data) at ($(activity) + (3,0)$) [fill=purple!30, draw] {Data};
+        \node (discussion) at ($(data) + (2,1.5)$) [fill=green!30, draw] {Discussion};
+        \node (theory) at ($(data) + (2,-1.5)$) [fill=red!30, draw] {Theory};
+
+        % Creative arrows
+        \draw [thick, ->] (activity) -- (data);
+        \draw [thick, ->] (data) edge[out=90, in=180] (discussion);
+        \draw [thick, ->] (discussion) edge[out=-45, in=45] (theory);
+
+        % Reflective arrows
+        \draw [thick, ->, dashed] (theory) edge[out=180, in=-90] (data);
+        \draw [thick, ->, dashed] (theory) edge[out=180, in=-90] (activity);
+        \draw [thick, ->, dashed] (discussion) edge[out=180, in=90] (activity);
+        \draw [thick, ->, dashed] (theory) edge[out=135, in=-135] (discussion);
+
+        % Key
+        \draw [thick, ->] ($(activity) + (-3,.25)$) -- ($(activity) + (-2.5,.25)$);
+        \node at ($(activity) + (-4, .25)$) {Production:};
+        \draw [thick, ->, dashed] ($(activity) + (-3,-.25)$) -- ($(activity) +
+        (-2.5,-.25)$);
+        \node at ($(activity) + (-4, -.25)$) {Reflection:};
+
+    \end{tikzpicture}
+    \centering
+    \caption{The active generation of data by students}
+    \label{fig:use_of_data}
+\end{figure}
+
+This pedagogic approach is used throughout the course (from the first lesson)
+and so after a few class meetings students are used to the high level of
+participation. Here are some examples of written feedback concerning the
+activities used in class.
+
+\begin{itemize}
+    \item Quote 1
+    \item Quote 2
+    \item Quote 3
+\end{itemize}
+
+Nonetheless at the start of the course certain class management
+techniques described in \cite{Rocca2010} are used. For example, the extension of
+the `waiting time' for responses to questions. For students to be active
+participants it is vital that they are given the time to do so.
+
+The activities described in Section \ref{sec:game_theory} are particular to game
+theory however the author does not feel that the general pedagogic strategy
+outlined in Figure \ref{fig:use_of_data} is constrained to a particular course.
+Similar activities could be devised in other subjects where students generate
+`data' than aids the contextualisation of theory so as to aspire to not only a
+constructive learning model but also a social one.
 

### 2015-06-30 paper/paper.tex
Reorganising graphical output
Moving pdf files in data to output subdirectory.
Making things look a bit more wordish.
More adjustments

@@
-\documentclass{article}
+\documentclass[12pt, a4paper]{article}
 
-\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
-%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
+%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
+\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
 %\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=authoryear]{biblatex}
 \addbibresource{library.bib}
+
+\usepackage{fullpage}
 
@@
 \usepackage{wordlike}  % Make this look like word made it
+%\usepackage{xcolor}
+%\usepackage{sectsty}
+%\sectionfont{\color{cyan}}
+%\subsectionfont{\color{cyan}}
 
@@
 \abstract{
-    This paper describes two active learning activities aiming to introduce
-    students to the theoretic concepts of best response dynamics and repeated
-    game analysis.
+    This paper describes two active learning activities which aims to introduce
+    students to the game theoretic concepts of best response dynamics and
+    repeated game analysis.
 
     An overview of some literature on active learning and the benefits therein
-    is also provided. This highlights that activities such as the one described
-    in this manuscript not only help engage students but more importantly
+    is provided. This highlights that activities such as the one described
+    in this manuscript, not only help engage students but more importantly
     improve their learning and understanding.
 
-    The final section of the work describes how these activities fit in the
-    pedagogic framework of a particular class. Students generate data that
-    can be used as context for the understanding of theoretic concepts. It is
-    suggested that this framework is not restricted to the subject of game
-    theory.
+    The final section of this work describes how these activities fit in the
+    pedagogic framework of a particular undergraduate mathematics class.
+    Students generate data that can be used as context for the understanding of
+    theoretic concepts. It is suggested that this framework is not restricted to
+    the subject of game theory.
 }
@@
 
-One could argue that all learning is active as students simply listening to a
-lecture are perhaps taking part in a `meaningful learning activity', however as
-stated in \cite{Bonwell1991} active learning is understood to imply that
-students:
+One could argue that all learning is active as simply listening to a lecture is
+perhaps taking part in a `meaningful learning activity', however as stated in
+\cite{Bonwell1991} active learning is understood to imply that students:
 
@@
 A variety of studies have highlighted the effectiveness of active learning
-\cite{Freeman2014, Hake1998, Prince2004}. These two papers are in fact meta studies
-evaluating the effectiveness an active student centred approach. Note that the
-definition used in \cite{Freeman2014} corresponds to simply any pedagogic
-approach in which students are not passive consumers of a lecture during the
-class meeting. Some examples of active learning in a variety of subjects include:
+\cite{Freeman2014, Hake1998, Prince2004}. These two papers are in fact meta
+studies evaluating the effectiveness of an active student centred approach. Note
+that the definition used in \cite{Freeman2014} corresponds to simply any
+pedagogic approach in which students are not passive consumers of a lecture
+during the class meeting. Some examples of active learning in a variety of
+subjects include:
 
@@
     \item Section \ref{sec:best_responses} will describe an in class activity
-        and software package used to introduce students to the topic of best
-        response dynamic \cite{Maschler2013}.
+        used to introduce students to the topic of best response dynamics and
+        dominated strategies \cite{Maschler2013}.
     \item Section \ref{sec:repeated_games} will describe an implementation of
@@
 
-These activities aim to introduce the student to the concepts and aspire to
-their curiosity as to the underlying mathematics. Note that if there is any
-doubt as to the effectiveness of active learning approaches, for example this paper
-(the only one that this author could identify) \cite{Andrews2011} identifies no
-such relationship are still beneficial to the students' learning.
-Indeed in \cite{Poropat2014}  the greatest predictors of
-academic performance are identified not as general intelligence \cite{Wright1905} but
-personality factors such as conscientiousness and openness.
+These activities aim to introduce participants to concepts and aspire to their
+curiosity as to the underlying mathematics. Note that if there is any doubt as
+to the effectiveness of active learning approaches, for example
+\cite{Andrews2011} which identifies no such relationship, inciting curiosity and
+engagement aare still beneficial to the students' learning.  Indeed in
+\cite{Poropat2014}  the greatest predictors of academic performance are
+identified not as general intelligence \cite{Wright1905} but personality factors
+such as conscientiousness and openness.
+
+Section \ref{sec:game_theory} will describe the activities and Section
+\ref{sec:summary} will detail how these fit in a more general pedagogic context.
+Finally, all source files for this paper (including data and the analysis) can
+be found at this url:
+\url{https://github.com/drvinceknight/Playing-games-a-case-study-in-active-learning}.
 
@@
 Game Theory as a topic is well suited to approaches that use activities
-involving students as players to introduce the concepts, rules and strategies
+involving participants as players to introduce the concepts, rules and strategies
 for particular games and/or theorems presented.
 
-In \cite{Brokaw2004} one such activity is presented: a game that allow players
+In \cite{Brokaw2004} one such activity is presented: a game that allows players
 to grasp the concept of common knowledge of rationality. Another good example is
@@
 reference (a YouTube playlist) all show that students are introduced to every
-concept through activity before discussing theory.
+concept through activity before discussing theory (this is akin to the framework
+discussed in Section \ref{sec:summary}.
 
 Just as the activity presented in \cite{Brokaw2004} the activities presented
-here are both suited for as an early introduction to the concepts (although the
-activity of Section \ref{sec:repeated_games} is potentially better suited to
-being used at a later stage). Furthermore, these activities have also been used
-as outreach activities for high school students with no knowledge of further
-mathematics.
+here are suited for an early introduction to the concepts (although the activity
+of Section \ref{sec:repeated_games} is potentially better suited to being used
+at a later stage). Furthermore, these activities have also been used
+successfully as outreach activities for high school students with no knowledge
+of further mathematics.
 
-\subsection{Best response dynamics}\label{sec:best_responses}
+\subsection{Best response dynamics and dominated strategies}\label{sec:best_responses}
 
 The first step in this activity and potentially before any prior description of
-Game Theory students are invited to answer the following simple question:
+Game Theory is to invite participants to answer the following simple question:
 
@@
 
-Through discussion the class will usually arrive at the following consensus:
+Through discussion the participants will usually arrive at the following consensus:
 
@@
     \item A game must have a certain number \(N\geq 1\) of players;
-    \item Each player must have available to them a certain number of strategies
+    \item Each player must have available to them a certain set of strategies
         that define what they can do;
@@
 \cite{Maschler2013}. The main goal of this activity is to not only understand
-the vocabulary but also the important concept of response dynamics which aims
-to identify what is the best option given prior knowledge of all other players
-\cite{Maschler2013}. One particular game that can be analysed using base
+the vocabulary but also the important concept of best response dynamics which
+aims to identify what is the best option given prior knowledge of all other
+players \cite{Maschler2013}. A particular game that can be analysed using base
 response dynamics is often referred to:
@@
 
-A good description of the game and the human dynamics associated to the play is
-given in \cite{Nagel1995}.  The use of this game in teaching is not novel in
-game theory \cite{TheEconomicsNetwork2013}
-The rules are as follows:
+A good description of the game and the human dynamics associated to it is given
+in \cite{Nagel1995}.  The use of this game in teaching is not at all novel
+\cite{TheEconomicsNetwork2013}. The rules are as follows:
 
@@
     \item All players choose a number between 0 and 100;
-    \item The player whose choice was closest to \(\frac{2}{3}\) of the average
+    \item The player whose guess is closest to \(\frac{2}{3}\) of the average
         of the choices wins.
@@
 response dynamics students are handed a sheet of paper inviting them to write
-down a first play. After this initial play, a discussion is had that
+down a first guess. After this initial play, a discussion is had that
 demonstrates that the equilibrium for this game is for all players to guess 0.
@@
 during another class activity.
-Following this, the result shown in Figure \ref{fig:histogram_of_guess} are
-shown and discussed with the class.
+Following this, the results (corresponding to the results of Figure
+\ref{fig:histogram_of_guess}) are shown and discussed.
+This discussion usually revolves around the observation that not everyone acted
+rationally and second that some participants felt like they should `spoil' the
+game by guessing larger in the second round.
 
@@
 times collected the data. Figure \ref{fig:histogram_of_guess} shows the
-distribution of the guesses (depending on the round of play):
+distribution of the guesses (depending on the round of play).
 
@@
 
-The fact that the coefficient of the relationship is less than one highlights
-that the second guess is in general lower than the first guess. As can be seen
-in Figure \ref{fig:all_results} not all students reduce their guess. Figure
-\ref{fig:results_with_decreasing_guess} shows the results when removing these
-irrational moves. In this particular case the linear relationship is in fact
-stronger \(R^2=.43\):
+The fact that the coefficient of the relationship (\(.203\)) is less than one
+highlights that the second guess is in general lower than the first guess. As
+can be seen in Figure \ref{fig:all_results} not all students reduce their guess.
+Figure \ref{fig:results_with_decreasing_guess} shows the results when removing
+these irrational moves. In this particular case the linear relationship is in
+fact stronger \(R^2=.43\):
 
@@
 
-At the end of the activity, students are shown the graphical results and a
-discussion had about why the theoretic equilibrium was not the winner. This
-discussion usually revolves around the observation that not everyone acted
-rationally and second that some participants felt like they should `spoil' the
-game by guessing larger in the second round.
-
 Finally, if time permits (and depending on the level of the participants), the
@@
 would happen if more rounds were to be played. In particular it is possible to
-discuss ideas of convergence when generalising (\ref{eq:linear_relationship}) to
-be:
+discuss ideas of convergence (cobweb diagrams in particular) when generalising
+(\ref{eq:linear_relationship}) to be:
 
@@
 
-To summarise this activity:
+To summarise this activity has the following steps:
 
@@
 seated throughout). Nevertheless it allows the data used for the discussion of
-the theory to come directly from the participants and further more all students
+the theory to come directly from the participants. Further more all students
 are active participants and there are no difficulties with regards to
@@
 \cite{Maschler2013}. The mathematical details can be omitted from the initial
-description of the activity to the participants but for completeness it they are
+description of the activity to the participants but for completeness they are
 included here:
@@
 One of the most renowned repeated games is referred to as \textbf{Axelrod's
-tournament} which is what is recreated in this activity \cite{Axelrod1980a,
-Axelrod1980b}.
+tournament} \cite{Axelrod1980a, Axelrod1980b} which is what is recreated in this
+activity.
 
@@
 
-The row player has utility given by \(A\) and the column player has utilities
+The row player has utility given by \(A\) and the column player has utility
 given by \(B\).
@@
 activity of Section \ref{sec:best_responses}) participants are made aware of the
-concept of Nash equilibrium. This in turn can lead to a brief description of the
-tragic yet brilliant life of John Nash.
+concept of Nash equilibrium. (This in turn can lead to a brief description of the
+tragic yet brilliant life of John Nash).
 
@@
 
-The tournament is run with all participants present (even those not watching).
-All participants are invited to stand and confer in their teams. The importance
-of standing (as a physical activity) is noted in \cite{Donnelly2011} (whilst
-that reference is mainly concerned with the impact of activity on physical well
-being it also describes advantages in terms of concentration).  Before every
-round of every duel opposing teams are encouraged to discuss strategies, after
-which they do not face each other and following a prompt hold up a card
-indicating either \(C\) or \(D\).  Duels are recorded on the white board in a
-table similar to the one shown in Table \ref{tab:duel}, in which two strategies
-constantly cooperate (thus obtaining a utility of 3 in each round). Table
-\ref{tab:duel_1} shows an example where a strategy that is alternating plays
-against a strategy that always defects.
+The tournament is run with all participants present (even those not involved in
+a duel).  All participants are invited to stand and confer in their teams. The
+importance of standing (as a physical activity) is noted in \cite{Donnelly2011}
+(whilst that reference is mainly concerned with the impact of activity on
+physical well being it also describes advantages in terms of concentration).
+Before every round of every duel opposing teams are encouraged to discuss
+strategies, after which they face away from each other and following a prompt
+hold up a card indicating either \(C\) or \(D\).  Duels are recorded on a wall
+board in a table similar to the ones shown in Tables \ref{tab:duel} and
+\ref{tab:duel}.  Table \ref{tab:duel} shows two strategies which constantly
+cooperate (thus obtaining a utility of 3 in each round). Table \ref{tab:duel_1}
+shows an example where a strategy that is alternating plays against a strategy
+that always defects.  Figure \ref{fig:white_board} shows a photo of a final
+board for a particular implementation of this activity.
 
@@
     \centering
-    \begin{tabular}{ccccc}
+    \begin{tabular}{lccccc}
         \toprule
-        3&6&9&12&15\\
+        Tit For Tat&3&6&9&12&15\\
         \midrule
-        3&6&9&12&15\\
+        Cooperator&3&6&9&12&15\\
         \bottomrule
@@
     \centering
-    \begin{tabular}{ccccc}
+    \begin{tabular}{lccccc}
         \toprule
-        5&6&11&12&17\\
+        Defector&5&6&11&12&17\\
         \midrule
-        0&1&1&2&2\\
+        Alternator&0&1&1&2&2\\
         \bottomrule
@@
 \end{table}
-
-Figure \ref{fig:white_board} shows a photo of a final board for a particular
-implementation of this activity.
 
@@
 \cite{Axelrod1980a, Axelrod1980b}. The interesting fact of repeated games and
-one that becomes apparent to participants through the activity is that whilst
-repeating the stage Nash equilibrium (always defect) is indeed a Nash
-equilibrium for the repeated games, this equilibrium is not unique as
-reputation now has a part to play.
+one that usually becomes apparent to participants through the activity is that
+whilst repeating the stage Nash equilibrium (always defect) is indeed a Nash
+equilibrium for the repeated games, this equilibrium is not unique as reputation
+now has a part to play.
 
-Note that if students do not realise this it is important to remind them that
-the goal is not to win each duel but to obtain a high score. Often during the
-tournament one team will (during the pre round discussion) exclaim:
+Note that if participants do not realise that this it is important to remind
+them that the goal is not to win each duel but to obtain a high score overall.
+Often during the tournament one team will (during the pre round discussion)
+exclaim:
 
@@
 constrained. From a pedagogic point of view however, having participants observe
-the duels often leads to a much more engaged discussion (after as well as during
+the duels often leads to a much more engaged discussion (after, as well as during
 the activity).
@@
 Further to the fun had by participants, the theoretic discussion about repeated
-games can be placed in the exact context of the tournament that was just played.
+games can be placed in the exact context of the tournament that has just been
+played.
 
@@
         another round (this can be randomly sampled).
-    \item \textbf{Markov games}: the two random game states can be a true game
+    \item \textbf{Markov games}: two random game states can be a true game
         and an absorbing game so that this corresponds to an infinite game with
         discounting.
-    \item \textbf{Evolutionary games}: the two random game states can be a true game
-        and an absorbing game so that this corresponds to an infinite game with
-        discounting.
+    \item \textbf{Evolutionary games}: this follows from considering strategies
+        in an evolutionary context as showin in \ref{fig:evolutionary_axelrod}.
 \end{itemize}
@@
 particular theoretic results and how they correspond (or not) to the behaviour
-exhibited during the activity. Furthermore, this encourages an immediate
+exhibited during the activity. Furthermore, this encourages immediate
 feedback with regards to student comprehension which can be reactively
@@
 participation. Here are some examples of written feedback concerning the
-activities used in class.
+activities used in class:
 
 \begin{itemize}
-    \item Quote 1
-    \item Quote 2
-    \item Quote 3
+    \item ``Classes were fun.''
+    \item ``The games helped make the content interesting.''
+    \item ``This course teaches me to not trust my classmates.''
 \end{itemize}
 
-Nonetheless at the start of the course certain class management
-techniques described in \cite{Rocca2010} are used. For example, the extension of
-the `waiting time' for responses to questions. For students to be active
-participants it is vital that they are given the time to do so.
+Nonetheless at the start of the course certain class management techniques
+described in \cite{Rocca2010} are used. For example, the extension of the
+`waiting time' for responses to questions is implemented. For students to be
+active participants it is vital that they are given the time to do so.
 
@@
 theory however the author does not feel that the general pedagogic strategy
-outlined in Figure \ref{fig:use_of_data} is constrained to a particular course.
+outlined in Figure \ref{fig:use_of_data} is constrained to a particular subject.
 Similar activities could be devised in other subjects where students generate
-`data' than aids the contextualisation of theory so as to aspire to not only a
+`data' that aids the contextualisation of theory so as to aspire to not only a
 constructive learning model but also a social one.

### 2015-06-30 paper/images/use_of_data.tex
Moving tikz code to standalone files.

--- 2015-06-30 paper/paper.tex
@@
-\documentclass{article}
+\documentclass{standalone}
+% \documentclass{article}
 
-\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
-%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
-%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=authoryear]{biblatex}
-\addbibresource{library.bib}
-
-\usepackage{amsmath}
-\usepackage{hyperref}
 \usepackage{tikz}
-\usepackage{booktabs}
-\usepackage{subcaption}
-
-\usepackage{wordlike}  % Make this look like word made it
-
-\title{Playing Games: A Case Study in Active Learning Applied to Game Theory}
-\author{Vince Knight}
-\date{\today}
+\usetikzlibrary{calc}
 
@@
 
-\maketitle
+    \begin{tikzpicture}
+        % Nodes
+        \node (activity) at (0,0) [fill=cyan!30, draw] {Activity};
+        \node (data) at ($(activity) + (3,0)$) [fill=purple!30, draw] {Data};
+        \node (discussion) at ($(data) + (2,1.5)$) [fill=green!30, draw] {Discussion};
+        \node (theory) at ($(data) + (2,-1.5)$) [fill=red!30, draw] {Theory};
 
-\abstract{
-A paper about active learning and using some example of this in a class on Game Theory
-}
+        % Creative arrows
+        \draw [thick, ->] (activity) -- (data);
+        \draw [thick, ->] (data) edge[out=90, in=180] (discussion);
+        \draw [thick, ->] (discussion) edge[out=-45, in=45] (theory);
 
-\section{Introduction}
+        % Reflective arrows
+        \draw [thick, ->, dashed] (theory) edge[out=180, in=-90] (data);
+        \draw [thick, ->, dashed] (theory) edge[out=180, in=-90] (activity);
+        \draw [thick, ->, dashed] (discussion) edge[out=180, in=90] (activity);
+        \draw [thick, ->, dashed] (theory) edge[out=135, in=-135] (discussion);
 
-Modern pedagogic theories as to how learning takes place such as constructivism
-and socialism \cite{Illeris2009, Jordan2008a}, indicate that an \textbf{active
-learning} approach is of benefit to student learning.  As stated in
-\cite{Prince2004} there are a variety of complementary definitions of active
-learning, however the general definition given in \cite{Prince2004} is the one
-assumed in this paper:
+        % Key
+        \draw [thick, ->] ($(activity) + (-3,.25)$) -- ($(activity) + (-2.5,.25)$);
+        \node at ($(activity) + (-4, .25)$) {Production:};
+        \draw [thick, ->, dashed] ($(activity) + (-3,-.25)$) -- ($(activity) +
+        (-2.5,-.25)$);
+        \node at ($(activity) + (-4, -.25)$) {Reflection:};
 
-\begin{quote}
-``Active learning is generally defined as any instructional method that engages
-students in the learning process. In short active learning requires students to
-do meaningful learning activities and think about what they are doing.''
-\end{quote}
+    \end{tikzpicture}
 
-One could argue that all learning is active as students simply listening to a
-lecture are perhaps taking part in a `meaningful learning activity', however as
-stated in \cite{Bonwell1991} active learning is understood to imply that
-students:
-
-\begin{itemize}
-    \item read, write, discuss, or engage in solving problems;
-    \item engage in higher order tasks such as analysis, synthesis and
-        evaluation.
-\end{itemize}
-
-A variety of studies have highlighted the effectiveness of active learning
-\cite{Freeman2014, Hake1998, Prince2004}. These two papers are in fact meta studies
-evaluating the effectiveness an active student centred approach. Note that the
-definition used in \cite{Freeman2014} corresponds to simply any pedagogic
-approach in which students are not passive consumers of a lecture during the
-class meeting. Some examples of active learning in a variety of subjects include:
-
-\begin{itemize}
-    \item The flipped learning environment in a Physics class: \cite{Bates}.
-    \item Inquiry based learning for the instruction of differential equations:
-        \cite{Kwon2005}.
-    \item Using collaborative learning in a pharmacology class:
-        \cite{Depaz2008}.
-\end{itemize}
-
-The above sources (and references therein) generally discuss the pedagogic
-approach from a macroscopic point of view with regards to the course considered.
-This manuscript will give a detailed description of two particular active
-learning activities used in the instruction of Game Theoretic concepts:
-
-\begin{itemize}
-    \item Section \ref{sec:best_responses} will describe an in class activity
-        and software package used to introduce students to the topic of best
-        response dynamic \cite{Maschler2013}.
-    \item Section \ref{sec:repeated_games} will describe an implementation of
-        Axelrod's tournament \cite{Axelrod1980a, Axelrod1980b}.
-\end{itemize}
-
-These activities aim to introduce the student to the concepts and aspire to
-their curiosity as to the underlying mathematics. Note that if there is any
-doubt as to the effectiveness of active learning approaches, for example this paper
-(the only one that this author could identify) \cite{Andrews2011} identifies no
-such relationship are still beneficial to the students' learning.
-Indeed in \cite{Poropat2014}  the greatest predictors of
-academic performance are identified not as general intelligence \cite{Wright1905} but
-personality factors such as conscientiousness and openness.
-
-\section{An exemplar: a course in game theory}\label{sec:game_theory}
-
-Game Theory as a topic is well suited to approaches that use activities
-involving students as players to introduce the concepts, rules and strategies
-for particular games and/or theorems presented.
-
-In \cite{Brokaw2004} one such activity is presented: a game that allow players
-to grasp the concept of common knowledge of rationality. Another good example is
-\cite{Polak2008}: Yale's Professor Polak's course, the videos available at that
-reference (a YouTube playlist) all show that students are introduced to every
-concept through activity before discussing theory.
-
-Just as the activity presented in \cite{Brokaw2004} the activities presented
-here are both suited for as an early introduction to the concepts (although the
-activity of Section \ref{sec:repeated_games} is potentially better suited to
-being used at a later stage). Furthermore, these activities have also been used
-as outreach activities for high school students with no knowledge of further
-mathematics.
-
-\subsection{Best response dynamics}\label{sec:best_responses}
-
-The first step in this activity and potentially before any prior description of
-Game Theory students are invited to answer the following simple question:
-
-\begin{center}
-    \textbf{What is a game?}
-\end{center}
-
-Through discussion the class will usually arrive at the following consensus:
-
-\begin{itemize}
-    \item A game must have a certain number \(N\geq 1\) of players;
-    \item Each player must have available to them a certain number of strategies
-        that define what they can do;
-    \item Once all players have chosen their strategy, rules must specify what
-        the outcome is.
-\end{itemize}
-
-This corresponds to the general definition of a strategic form game
-\cite{Maschler2013}. The main goal of this activity is to not only understand
-the vocabulary but also the important concept of response dynamics which aims
-to identify what is the best option given prior knowledge of all other players
-\cite{Maschler2013}. One particular game that can be analysed using base
-response dynamics is often referred to:
-
-\begin{center}
-    \textbf{The two thirds of the average game.}
-\end{center}
-
-A good description of the game and the human dynamics associated to the play is
-given in \cite{Nagel1995}.  The use of this game in teaching is not novel in
-game theory \cite{TheEconomicsNetwork2013}
-The rules are as follows:
-
-\begin{itemize}
-    \item All players choose a number between 0 and 100;
-    \item The player whose choice was closest to \(\frac{2}{3}\) of the average
-        of the choices wins.
-\end{itemize}
-
-To make use of this game in class as an introduction to the concept of best
-response dynamics students are handed a sheet of paper inviting them to write
-down a first play. After this initial play, a discussion is had that
-demonstrates that the equilibrium for this game is for all players to guess 0.
-This is shown diagrammatically in Figure
-\ref{fig:rationalisation_of_two_thirds_game}.
-
-Following this discussion students are invited to play again and write down
-their second guess. All of the results are collected, the author has used paper
-forms but an automated approach could also be used. In general the input and
-analysis of the data takes less than 10 minutes and can be done by a helper
-during another class activity.
-Following this, the result shown in Figure \ref{fig:histogram_of_guess} are
-shown and discussed with the class.
-
-\begin{figure}[!hbtp]
-    \begin{center}
-        \begin{tikzpicture}[thick,scale=0.7, every node/.style={scale=0.7}]
-            % First level of play
-            \node (0) at (0,0) {$0$};
-            \node (100) at (10,0) {$100$};
-            \draw [thick] (0) -- (100);
-            \node [below] at (6.7,0) {$67$};
-
-            % Getting rid of dominated strategies
-            \foreach \x in {7, 7.3, 7.6, 7.9, 8.2, 8.5, 8.8, 9.1, 9.4}
-            {
-                \draw [blue!80, very thick] (\x,-.25) -- (\x + .2,.25);
-            }
-            \draw [very thick, blue!80] (9, -.5) edge[out=270,in=0,->] (7, -2);
-
-                % Second level of play
-                \node (0) at (0,-2) {$0$};
-                \node (67) at (6.7,-2) {$67$};
-                \draw [thick] (0) -- (67);
-                \node [below] at (4.4,-2) {$44$};
-
-                % Getting rid of dominated strategies
-                \foreach \x in {4.7, 5, 5.3, 5.6, 5.9, 6.2}
-                {
-                    \draw [blue!60, very thick] (\x,-2.25) -- (\x + .2,-1.75);
-                }
-                \draw [very thick, blue!60] (6, -2.5) edge[out=270,in=0,->] (4.7, -4);
-
-                    % Third level of play
-                    \node (0) at (0,-4) {$0$};
-                    \node (44) at (4.4,-4) {$44$};
-                    \draw [thick] (0) -- (44);
-                    \node [below] at (2.9,-4) {$29$};
-
-                    % Getting rid of dominated strategies
-                    \foreach \x in {3.2, 3.5, 3.8}
-                    {
-                        \draw [blue!40, very thick] (\x,-4.25) -- (\x + .2,-3.75);
-                    }
-
-                        % Final level of play
-                        \node at (2, -5) {\dots};
-                        \node (0) at (1,-6) [draw] {$0$};
-                        \draw [very thick, blue!40] (3.4, -4.5) edge[out=270,in=0,->] (1.5, -6);
-
-            \node at (8, -5) [draw] {Removing dominated strategies};
-        \end{tikzpicture}
-    \end{center}
-    \caption{Equilibrium behaviour in the two thirds of the average
-    game}\label{fig:rationalisation_of_two_thirds_game}
-\end{figure}
-
-The author has used this activity on a large number of occasions and at all
-times collected the data. Figure \ref{fig:histogram_of_guess} shows the
-distribution of the guesses (depending on the round of play):
-
-\begin{figure}[!hbtp]
-    \begin{subfigure}{.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{static/histogram_of_guesses.pdf}
-        \caption{Frequency of guesses depending on the round of play.}
-        \label{fig:histogram_of_guess}
-    \end{subfigure}
-    \begin{subfigure}{.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{static/jointplot_of_guesses.pdf}
-        \caption{Linear relationship between guesses of each round of play.}
-        \label{fig:jointplot_of_guess}
-    \end{subfigure}
-    \caption{Results from all data collected.}
-    \label{fig:all_results}
-\end{figure}
-
-We see that the second round (after the rationalisation of play described in
-Figure \ref{fig:rationalisation_of_two_thirds_game}) has guesses that are closer
-to the expected equilibrium behaviour.
-Figure \ref{fig:jointplot_of_guess} confirms this showing the linear
-relationship (albeit a weak one with \(R^2=.2\)):
-
-\begin{equation}
-    (\text{Second guess}) = .203\times(\text{First guess}) + 9.45
-    \label{eq:linear_relationship}
-\end{equation}
-
-The fact that the coefficient of the relationship is less than one highlights
-that the second guess is in general lower than the first guess. As can be seen
-in Figure \ref{fig:all_results} not all students reduce their guess. Figure
-\ref{fig:results_with_decreasing_guess} shows the results when removing these
-irrational moves. In this particular case the linear relationship is in fact
-stronger \(R^2=.43\):
-
-\begin{equation}
-    (\text{Second guess}) = .33\times(\text{First guess}) + 0.20
-    \label{eq:linear_relationship_for_increasing_guesses}
-\end{equation}
-
-\begin{figure}[!hbtp]
-    \begin{subfigure}{.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{static/histogram_of_guesses_removing_increasing_guesses.pdf}
-        \caption{Frequency of guesses depending on the round of play.}
-        \label{fig:histogram_of_guess}
-    \end{subfigure}
-    \begin{subfigure}{.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{static/jointplot_of_guesses_removing_increasing_guesses.pdf}
-        \caption{Linear relationship between guesses of each round of play.}
-        \label{fig:jointplot_of_guess}
-    \end{subfigure}
-    \caption{Results from data when removing increasing guesses.}
-    \label{fig:results_with_decreasing_guess}
-\end{figure}
-
-At the end of the activity, students are shown the graphical results and a
-discussion had about why the theoretic equilibrium was not the winner. This
-discussion usually revolves around the observation that not everyone acted
-rationally and second that some participants felt like they should `spoil' the
-game by guessing larger in the second round.
-
-Finally, if time permits (and depending on the level of the participants), the
-linear relationship of (\ref{eq:linear_relationship}) is used to discuss what
-would happen if more rounds were to be played. In particular it is possible to
-discuss ideas of convergence when generalising (\ref{eq:linear_relationship}) to
-be:
-
-\begin{equation}
-    \text{Guess}_{n+1} = .203\times\text{Guess}_n + 9.45
-    \label{eq:extrapolated_linear_relationship}
-\end{equation}
-
-To summarise this activity:
-
-\begin{enumerate}
-    \item Participants are explained the rules and play one round of the two
-        thirds of the average game.
-    \item A rationalisation and explanation of equilibrium behaviour is
-        described.
-    \item Participants play another round.
-    \item Results are analysed and discussed.
-\end{enumerate}
-
-This activity is still quite passive in terms of physical activity (participants are
-seated throughout). Nevertheless it allows the data used for the discussion of
-the theory to come directly from the participants and further more all students
-are active participants and there are no difficulties with regards to
-encouraging participation (references to these are discussed in \cite{Rocca2010}).
-
-\subsection{Repeated and random games}\label{sec:repeated_games}
-
-This activity is used to introduce students to the concepts of repeated games
-\cite{Maschler2013}. The mathematical details can be omitted from the initial
-description of the activity to the participants but for completeness it they are
-included here:
-
-A repeated game is played over discrete time periods. Each time period is
-indexed by \(0<t\leq T\) where \(T\) is the total number of periods.  In each
-period \(N\) players play a static game referred to as the \textbf{stage game}
-independently and simultaneously selecting actions.  Players make decisions in
-full knowledge of the \textbf{history} of the game played so far (ie the actions
-chosen by each player in each previous time period).  The payoff is defined
-as the sum of the utilities in each stage game for every time period.
-
-One of the most renowned repeated games is referred to as \textbf{Axelrod's
-tournament} which is what is recreated in this activity \cite{Axelrod1980a,
-Axelrod1980b}.
-
-Initially a description of the prisoner's dilemma \cite{Maschler2013} is given.
-The prisoner's dilemma is a simple two player game that is often used to
-introduce the very basic notions of game theory. It is described by the
-following two matrices:
-
-\[
-    A =
-    \begin{pmatrix}
-        3&5\\
-        0&1
-    \end{pmatrix}
-    \qquad
-    B =
-    \begin{pmatrix}
-        3&0\\
-        5&1
-    \end{pmatrix}
-\]
-
-The row player has utility given by \(A\) and the column player has utilities
-given by \(B\).
-The strategies available to each player are to cooperate: \(C\) or to defect:
-\(D\). Playing \(C\) corresponds to players choosing their first row/column and
-\(D\), the second row/column.
-
-Thus if both players cooperate they both receive a utility of 3, if one player
-defects, the defector gets a utility of 5 and the cooperator a utility of 0.
-Finally if both players defect they receive a utility of 1. As players (in this
-framework) aim to maximise their score, the Nash equilibrium for this game is
-for both players to defect.
-
-After describing this activity and in particular explaining the simple
-mathematical idea of \textbf{dominated strategy} (which is what is used in the
-activity of Section \ref{sec:best_responses}) participants are made aware of the
-concept of Nash equilibrium. This in turn can lead to a brief description of the
-tragic yet brilliant life of John Nash.
-
-At this point the activity is described:
-
-\begin{enumerate}
-    \item All participants will form four groups/teams;
-    \item Teams will \textit{duel} each other in repetitions of 5 to 8 rounds
-        (depending on available time).
-    \item All teams will play in a round robin tournament with cumulative scores
-        being recorded.
-    \item The victorious team will be the team with the highest total score.
-\end{enumerate}
-
-The tournament is run with all participants present (even those not watching).
-All participants are invited to stand and confer in their teams. The importance
-of standing (as a physical activity) is noted in \cite{Donnelly2011} (whilst
-that reference is mainly concerned with the impact of activity on physical well
-being it also describes advantages in terms of concentration).  Before every
-round of every duel opposing teams are encouraged to discuss strategies, after
-which they do not face each other and following a prompt hold up a card
-indicating either \(C\) or \(D\).  Duels are recorded on the white board in a
-table similar to the one shown in Table \ref{tab:duel}, in which two strategies
-constantly cooperate (thus obtaining a utility of 3 in each round). Table
-\ref{tab:duel_1} shows an example where a strategy that is alternating plays
-against a strategy that always defects.
-
-\begin{table}[!htbp]
-    \caption{Playing Tit For Tat against Cooperator}
-    \centering
-    \begin{tabular}{ccccc}
-        \toprule
-        3&6&9&12&15\\
-        \midrule
-        3&6&9&12&15\\
-        \bottomrule
-    \end{tabular}
-    \label{tab:duel}
-\end{table}
-
-\begin{table}[!htbp]
-    \caption{Playing Alternator against Defector}
-    \centering
-    \begin{tabular}{ccccc}
-        \toprule
-        5&6&11&12&17\\
-        \midrule
-        0&1&1&2&2\\
-        \bottomrule
-    \end{tabular}
-    \label{tab:duel_1}
-\end{table}
-
-Figure \ref{fig:white_board} shows a photo of a final board for a particular
-implementation of this activity.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.5\textwidth]{static/white_board.jpg}
-    \caption{A photo of an actual implementation of the tournament.}
-    \label{fig:white_board}
-\end{figure}
-
-The names of the strategies shown in Tables \ref{tab:duel} and \ref{tab:duel_1}
-are strategies that were used in the original tournaments run by Axelrod
-\cite{Axelrod1980a, Axelrod1980b}. The interesting fact of repeated games and
-one that becomes apparent to participants through the activity is that whilst
-repeating the stage Nash equilibrium (always defect) is indeed a Nash
-equilibrium for the repeated games, this equilibrium is not unique as
-reputation now has a part to play.
-
-Note that if students do not realise this it is important to remind them that
-the goal is not to win each duel but to obtain a high score. Often during the
-tournament one team will (during the pre round discussion) exclaim:
-
-\begin{quote}
-   ``We will cooperate until you defect, at which point we will defect
-throughout''
-\end{quote}
-
-Without realising it the participants have described a well known strategy
-(\textbf{Grudger}) which takes in to account the entire history of play.
-
-This activity can be complemented with a demonstration of software that allows
-for the rapid simulation of Axelrod's tournament
-\cite{Axelrod-Pythonprojectteam2015}. Figure \ref{fig:evolutionary_axelrod}
-shows the performance of the strategies when put in an evolutionary context.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.6\textwidth]{static/basic_strategies-reproduce.pdf}
-    \caption{Repeated games in an evolutionary context.}
-    \label{fig:evolutionary_axelrod}
-\end{figure}
-
-One of the inconsistancies of this approach is that all participants observe the
-play by all the teams. Whilst from a mathematical perspective reputation is
-inferred to mean the reputation gained during a particular duel, this has the
-effect of teams being able to observe how other teams seem to play. A true
-replication of Axelrod's tournament would not allow for this. One possibility
-would invite participants to leave the room which might be logistically
-constrained. From a pedagogic point of view however, having participants observe
-the duels often leads to a much more engaged discussion (after as well as during
-the activity).
-
-This activity is usually very enjoyable and leads to a lively discussion.
-Further to the fun had by participants, the theoretic discussion about repeated
-games can be placed in the exact context of the tournament that was just played.
-
-This activity can be used to introduce further game theoretic topics with
-slight modifications:
-
-\begin{itemize}
-    \item \textbf{Infinitely repeated games with discounting}: the discount
-        factor can be interpreted as a probability of the duel continuing for
-        another round (this can be randomly sampled).
-    \item \textbf{Markov games}: the two random game states can be a true game
-        and an absorbing game so that this corresponds to an infinite game with
-        discounting.
-    \item \textbf{Evolutionary games}: the two random game states can be a true game
-        and an absorbing game so that this corresponds to an infinite game with
-        discounting.
-\end{itemize}
-
-\section{Summary}
-
-\begin{itemize}
-    \item Give some examples of feedback.
-    \item Mention how methods could be applied to other courses.
-    \item Certain class management ideas (mainly that I will not speak first a
-        lot of the time) <- Not sure if this is useful.
-\end{itemize}
-
-\printbibliography
 \end{document}

### 2015-06-30 paper/paper.tex
Moving tikz code to standalone files.

@@
 \usetikzlibrary{calc}
+\usepackage{standalone}
 
@@
 \begin{figure}[!hbtp]
-    \begin{center}
-        \begin{tikzpicture}[thick,scale=0.7, every node/.style={scale=0.7}]
-            % First level of play
-            \node (0) at (0,0) {$0$};
-            \node (100) at (10,0) {$100$};
-            \draw [thick] (0) -- (100);
-            \node [below] at (6.7,0) {$67$};
-
-            % Getting rid of dominated strategies
-            \foreach \x in {7, 7.3, 7.6, 7.9, 8.2, 8.5, 8.8, 9.1, 9.4}
-            {
-                \draw [blue!80, very thick] (\x,-.25) -- (\x + .2,.25);
-            }
-            \draw [very thick, blue!80] (9, -.5) edge[out=270,in=0,->] (7, -2);
-
-                % Second level of play
-                \node (0) at (0,-2) {$0$};
-                \node (67) at (6.7,-2) {$67$};
-                \draw [thick] (0) -- (67);
-                \node [below] at (4.4,-2) {$44$};
-
-                % Getting rid of dominated strategies
-                \foreach \x in {4.7, 5, 5.3, 5.6, 5.9, 6.2}
-                {
-                    \draw [blue!60, very thick] (\x,-2.25) -- (\x + .2,-1.75);
-                }
-                \draw [very thick, blue!60] (6, -2.5) edge[out=270,in=0,->] (4.7, -4);
-
-                    % Third level of play
-                    \node (0) at (0,-4) {$0$};
-                    \node (44) at (4.4,-4) {$44$};
-                    \draw [thick] (0) -- (44);
-                    \node [below] at (2.9,-4) {$29$};
-
-                    % Getting rid of dominated strategies
-                    \foreach \x in {3.2, 3.5, 3.8}
-                    {
-                        \draw [blue!40, very thick] (\x,-4.25) -- (\x + .2,-3.75);
-                    }
-
-                        % Final level of play
-                        \node at (2, -5) {\dots};
-                        \node (0) at (1,-6) [draw] {$0$};
-                        \draw [very thick, blue!40] (3.4, -4.5) edge[out=270,in=0,->] (1.5, -6);
-
-            \node at (8, -5) [draw] {Removing dominated strategies};
-        \end{tikzpicture}
-    \end{center}
+    \centering
+        \includestandalone[width=.6\textwidth]{images/rationalisation_of_two_thirds_game}
     \caption{Equilibrium behaviour in the two thirds of the average
@@
 \begin{figure}[!hbtp]
-    \begin{tikzpicture}
-        % Nodes
-        \node (activity) at (0,0) [fill=cyan!30, draw] {Activity};
-        \node (data) at ($(activity) + (3,0)$) [fill=purple!30, draw] {Data};
-        \node (discussion) at ($(data) + (2,1.5)$) [fill=green!30, draw] {Discussion};
-        \node (theory) at ($(data) + (2,-1.5)$) [fill=red!30, draw] {Theory};
-
-        % Creative arrows
-        \draw [thick, ->] (activity) -- (data);
-        \draw [thick, ->] (data) edge[out=90, in=180] (discussion);
-        \draw [thick, ->] (discussion) edge[out=-45, in=45] (theory);
-
-        % Reflective arrows
-        \draw [thick, ->, dashed] (theory) edge[out=180, in=-90] (data);
-        \draw [thick, ->, dashed] (theory) edge[out=180, in=-90] (activity);
-        \draw [thick, ->, dashed] (discussion) edge[out=180, in=90] (activity);
-        \draw [thick, ->, dashed] (theory) edge[out=135, in=-135] (discussion);
-
-        % Key
-        \draw [thick, ->] ($(activity) + (-3,.25)$) -- ($(activity) + (-2.5,.25)$);
-        \node at ($(activity) + (-4, .25)$) {Production:};
-        \draw [thick, ->, dashed] ($(activity) + (-3,-.25)$) -- ($(activity) +
-        (-2.5,-.25)$);
-        \node at ($(activity) + (-4, -.25)$) {Reflection:};
-
-    \end{tikzpicture}
     \centering
+    \includestandalone[width=.6\textwidth]{images/use_of_data}
     \caption{The active generation of data by students}

### 2015-07-22 paper/paper.tex
Setting up things to ease the creation of .docx
Giving up on wordifying.
Tidying up final version
- Fixing issue with full page (do not use \abstract{}...)
- Including acknowledgements to Zoe for help with Word
- link to twothirds library

@@
-\documentclass[12pt, a4paper]{article}
-
-%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
-\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
-%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=authoryear]{biblatex}
-\addbibresource{library.bib}
+\documentclass{article}
 
 \usepackage{fullpage}
+\usepackage{parskip}
 
@@
 
-\usepackage{wordlike}  % Make this look like word made it
-%\usepackage{xcolor}
-%\usepackage{sectsty}
-%\sectionfont{\color{cyan}}
-%\subsectionfont{\color{cyan}}
-
 % Diagrams
@@
 \usepackage{standalone}
+
+\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
+\addbibresource{library.bib}
 
@@
 
-\abstract{
+\begin{abstract}
     This paper describes two active learning activities which aims to introduce
@@
     the subject of game theory.
-}
+\end{abstract}
 
@@
 encouraging participation (references to these are discussed in \cite{Rocca2010}).
+
+At the time of writing, software is being written to help quickly analyse plays of the game (and produce the graphs seen above).
+Documentation for this can be found here: \url{http://twothirds.readthedocs.org/}.
 
@@
 
+\textbf{Acknowledgements}
+
+The author would like to thank Dr Zo{\"e} Prytherch for her help with the typesetting of the published version of this manuscript.
+
 \printbibliography
